On the Synchronization Power of the OpenFlow Data Plane

### 2015-05-26 inband-sync.tex
typos again
typos again, sorry

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. \liron{we need to discuss about this, I am not sure this description is accurate.}
In the mask, certain header fields, e.g., port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
Certain field, such as \emph{src}, \emph{dst}, \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
field for performing conditional operations on  its content.   
For examples, \texttt{port=10.1.14.0, ff.ff.ff.f0} matches all packets
with source addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.

@@

\begin{algorithm}[h]
    \caption{$\textit{write}(\addr,k)$}
    \label{alg:write}
    \begin{algorithmic}[1]
    %\Require  id $i$.
%    \Ensure
    		\State $value \gets \addr$
    		\State $mask \gets  \texttt{1$\ldots$1}. \texttt{1$\ldots$1}.$
    		\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets k$
    		\State $flag \gets 0$
    		\State $cmd\gets \emph{FlowMod}(match, op = \add, flag, action) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}

>>>>

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. \liron{we need to discuss about this, I am not sure this description is accurate.}
In the mask, certain header fields, e.g., TCP or UDP port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
Certain fields, such as \emph{ipv4\_src }, \emph{ipv4\_dst}, \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
field for performing conditional operations on  its content.   
For example, \texttt{ipv4\_src=10.1.14.0, ff.ff.ff.f0} matches all packets
with source IP addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.

@@

\begin{algorithm}[h]
    \caption{$\textit{write}(\addr,k)$}
    \label{alg:write}
    \begin{algorithmic}[1]
    %\Require  id $i$.
%    \Ensure
    		\State $value \gets \addr$
    		\State $mask \gets  \texttt{1$\ldots$1}. \texttt{1$\ldots$1}$
    		\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets k$
    		\State $flag \gets 0$
    		\State $cmd\gets \emph{FlowMod}(match, op = \add, flag, action) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}
